---
title: "Carbon Dioxide Emissions and Gross Domestic Product"
author: "Marijus Brazickas"
date: "5/28/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(gridExtra)
library(UsingR)
library(ggplot2)
```

## Introduction

Determining the pollution of countries by measuring the carbon dioxide ($CO_2$) emission levels and its relation to country's standard of living. 

A data set contains Gross Domestic Product (GDP), a measure of a country's economic output that accounts for its number of people (GDP per capita), and carbon dioxide ($CO_2$) emissions for 26 countries.

This data set frame contains the following columns:

- **GDP**
a numeric vector

- **perCapita**
a numeric vector

- **CO2**
a numeric vecto

## Table of dataset

```{r, echo=FALSE, comment = ""}
head(emissions, n=10)
```

## Summary of dataset
```{r, echo=FALSE, comment = ""}
summary(emissions)
```


## GDP relation to CO2 levels by country
```{r, echo=FALSE}
data(emissions)
data=(head(emissions, 26))

g1 <- ggplot(data=emissions, aes(x=GDP, y=CO2, color=CO2)) + geom_point(size=3.5) + labs(title="CO2 vs GDP") + geom_rug(col="steelblue",alpha=0.1, size=1.5) + geom_smooth(stat = 'smooth', color = 'Green', method = 'loess', formula = y ~ x) + 
            geom_text(
                label=rownames(data), 
                #hjust = 1.19, nudge_x = 0.25, 
                vjust = 1.4, nudge_y = 0.5,colour = "darkred",
                check_overlap = T
        
            ) 
       g1
```

## Emission levels of CO2, GDP, GDP per Capita 
```{r, echo=FALSE}
pairs(emissions[,1:3], pch = 19, col="green")
```





